Manuscript Outline

### 2018-10-03 Manuscript/results_outline.Rmd
edits

>>>>

* Summary of data
   + How many TADs
   + How many genomic bins
   + What genomic elements were used

* Results of class imbalance
   + which technique performed best?

* Results for including distance predictors?
   + results for model with just distance
   + results for model with both types
   + compare 
   + results from normalization techniques

* Results from classification algorithms
   + MLR
   + LASSO
   + ENET
   + RF
   + GBM
   + SVM 
   + Naiive Bayes
   + Compare

# Discussion

* State the results that were interesting 
   - Specific to each cell line/tfbs
   - Then results all together
* State how much better models using our pipeline performed compared to Mourad
   - Was it due to the model choice or the use of distance features?
* Limitations/Future
   - Mention the need for HiC experiments using higher resolutions
   - Experimenting with TAD data using other methods
   - Exploring other cell lines
